\setLTR
\maketitle

\section{Basic Info}
\begin{minipage}[t]{.5\linewidth}
\begin{tabular}{rp{.75\linewidth}}
\baselineskip=20pt
\email{} :   & \href{mailto:kirilurivsky@gmail.com}{kirilurivsky@gmail.com}\\
\phone{} : &\href{tel:972525470608}{(+972) 52 547 0608} \\
\end{tabular}
\end{minipage}
\begin{minipage}[t]{.5\linewidth}
\begin{tabular}{rl}
\linkedin{} : &\href{https://www.linkedin.com/in/kiril-u}{https://linkedin.com/in/kiril-u}\\
\location{} : &\href{https://goo.gl/maps/MSacjpSy7vZSKykP7}{Ashdod, South District}                                                                          
\end{tabular}
\end{minipage}

\input abstract

\input learning-skills

\section{Formal Education}

\entry{2019}
{Master of Arts, Educational Psychology (Expected); The Max Stern Yezreel Valley College, Jezreel Valley}
{\begin{itemize}
\item \textbf{Field}
        \item  Intern educational psychologist at a special-ed kindergarten and a high school in Afula.  
                \item Consultation for pedagogic and managerial staff of educational establishments.
                \item  Parental and teacher guidance
\item \textbf{Research}
                \item  Assessment of students' scholarly needs and hardships using and psychometrically sound diagnostic  instruments. 
                \item A highlight of academic interest and a current empirical pursuit includes \href{https://tinyurl.com/ADHD-Coping-Seminar}{research on ADHD and learning disabilities} across modalities of functioning and development from childhood to maturity. 
                \item Graduate thesis on remote learning and differences in academic achievment and socio-emotional functioning is being written under the supervision and advise of \href{https://www.researchgate.net/scientific-contributions/Orrie-Dan-2172412162}{Dr. Dan Orrie}.
   \end{itemize}}
{}

\entry{2015--2018}
{\href{https://www.dropbox.com/s/pcm0mybvgi85ma0/BA-Psych.pdf?dl=0}{Bachelor of Arts, Psychology and Multidisciplinary Studies, \textit{Summa Cum Laude}}, 95.00; Ben-Gurion University of the Negev}{- Rector's Award, Summa Cum Laude (2018) \\
- Department Chair’s Excellency Award (2017) \\
Minors in Philosophy and the Interdisciplinary Approach to Conflict and Negotiation.}
% {Dream psychoanalysis, the ethics of experimentation on animal subjects, and familial discord onset at childhood were some points of scholastic interest and praise at the time. 

\subsection{Additional Certifications}
\entry{2009--2010}
{\href{https://www.dropbox.com/s/csphxdynjdg3ze2/computer-technitian-certificate.jpg?dl=0}{Computer Technician Course, IQline, Academy of Sciences and Arts}}
{Diagnosis, repair, and maintenance of hardware and software components of computer systems and small networks}
{}

\section{Workplace Experience and Military Service}

\entry{2018--2019}
{Rehabilitation Coordinator at Kidum Rehabilitation Projects at Beit Kinneret, Ashdod.}
{Oversaw a variety of professional assignments to assist and provide services such as casework, treatment, outreach development, and referrals to psychiatric patients by arranging, scheduling, authorizing, and monitoring accommodation services.}
{}

\entry{2013--2015} 
{\textbf{Security Guard} at Reshef Security Ltd.,} 
{2015 - Bank Leumi's office buildings in Lod and Rishon LeZion. \\
2013 - Flying Cargo Group logistics' centers at Kannot Industrial Zone}
{\href{https://www.dropbox.com/s/kr5rcui1zgp35i0/recommendation-letter-security-guard.jpg?dl=0}{See recommendation letter.}}

\entry{2013--2014} 
{\textbf{NCO of Casualty Assistance} at the Israeli Defense Force in the Combat Engineering Corps} 
{positioned at GOC Army Headquarters as a liaison for medical, social, and memorial services provided for wounded or fallen soldiers, and their grieving families.}
{}

\section{Languages}

\entry{Human}
{\textbf{English, Hebrew, Russian}}
{Highly proficient in all three, capable of using either one interchangeably and befittingly to situational context and with great concern towards keeping discourse pleasant and culturally sensitive.}
{}

\entry{Machine}
{Computer}
{- bash and other GNU Project related and POSIX compliant shell CLIs \\
- A myriad of markup languages including \href{https://github.com/kiril-u/cv/blob/main/cv-a/main.tex}{\LaTeX/\XeTeX}, Markdown, XML, and HTML. \\
- some superficial knowledge of C, Java and JavaScript.} \\
{}
\section{Volunteer Work}


\entry{2017--2018}
{\textbf{Mental Health Assistant} at Clalit's Mental Health Center, Eilat}
{provided guidance, emotional support, and helped with development of self-sufficiency skills for child and teenage outpatients}
{}

\entry{2015--2018}
{\textbf{Mentorship at Perach}, Eilat}
{provided consultation and assistance for children at risk for matters of emotional, familial, educational, and social disadvantage}
{} 
\unsetLTR
