% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{latexsym, hyperref}
\begin{document}

\name{Hawk Weisman}
% \address used twice to have two lines of address
\address{990 First St, Meadville, PA, 16335}
\address{814-853-1501 | weismanm@allegheny.edu}

 
\begin{resume}
 
\section{EDUCATION} {\sl Bachelor of Science} \\
                Double Major in Applied Computing \& Environmental Studies \\
                % \sl will be bold italic in New Century Schoolbook (or
	            % any postscript font) and just slanted in
	           	% Computer Modern (default) font
                Allegheny College, Meadville, PA \\
                expected 2016
 
\section{COMPUTER \\ SKILLS} 
                Proficient programming skills in Java, Python, and C. \\
                Experience with Python-based technical computing environments such as IPython and Anaconda \\
                Experience with statistical analysis and visualization using tools such as \texttt{numpy}, \texttt{pandas}, \texttt{scipy}, and \texttt{matplotlib}. \\
                Experience with test automation, including advanced technologies such as code coverage and mutation analysis. \\
                Proficient with the use of \TeX/\LaTeX for document preparation. \\
                Familiar with the use of software engineering tools including version control, automated build systems, and continuous integration.

\section{OTHER \\ SKILLS}
                Knowledge of modern software engineering techniques and methodologies, with a focus on agile software development.\\
                Strong knowledge of experimental design and research methods in the biological and environmental sciences. \\
                Familiar with the use of geospatial technologies such as GIS, GPS, and remote sensing.
                Knowledge of and experience working with hydroponics and other soilless agriculture growing systems.\\
                Familiarity with biofuels and other sustainable energy technologies.

\section{WORK \\ EXPERIENCE} 
                {\sl Aquaponics Technician} \hfill Winter Break 2013 \\
                Environmental Science Department, Alllegheny College, Meadville, PA
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                    \item Responsible for independently maintaining multiple decorative and production aquaponics systems.
                    \item Performed maintenance tasks such as cleaning filters, feeding fish, and maintaining water levels.
                \end{itemize}
 
                {\sl Darkroom Technician} \hfill            2012-2013 \\
                Art Department, Allegheny College
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                    \item Responsible for preparing chemicals and maintaining a well-stocked darkroom, as well as ensuring workspace cleanliness.
                    \item Assisted and instructed art students in the use of darkroom materials and techniques.
                 \end{itemize} 

                {\sl Computer Art Studio Technician} \hfill        2012-2013 \\
                Art Department, Allegheny College
                  \begin{itemize} \itemsep -2pt %reduce space between items
                   \item Instructed other students in the use of computer art tools, such as drawing tablets, digital video cameras, and large-format printers.
                   \item Instructed other students in the use of software such as Photoshop, Illustrator, and Final Cut.
                   \item Diagnosed and repaired technical difficulties with studio equipment.
                   \end{itemize} 
 
\section{PROJECTS \\ AND RESEARCH}
        
                {\sl Filesystem Traversal Study} \hfill Ongoing (began Spring 2014) \\
                CMPSC440, Computer Science Department, Allegheny College
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                    \item Independently organized a research project to collect and analyze filesystem data.
                    \item Programmed data-collection tools in Python.
                    \item Prepared an IPython notebook to analyze and visualize data.
                    \item Encouraged other students to voluntarily contribute datasets.
                    \item Project available at \url{https://github.com/hawkw/traverse}
                \end{itemize}

                {\sl Knightingale Twitter Analysis System} \hfill Fall 2013 \\
                CMPSC290, Computer Science Department, Allegheny College
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                    \item Collaborated with other students to create an open-source software system to analyze Twitter account archive data.
                    \item Responsible for programming analytics and visualization, input/output, and unit testing.
                    \item Contributed a majority of Java code to the project.
                    \item Practiced Agile software development techniques.
                    \item Project available at \url{https://github.com/TeamKnightengale/Knightingale}
                \end{itemize}

                {\sl Switchgrass Biofuel Study} \hfill Spring 2013 \\
                ENVSC210, Environmental Science Department, Allegheny College
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                    \item Participated in an ongoing study to assess the viability of switchgrass pellets as a biofuel and industrial adsorbent.
                    \item Contributed to experimental design, implementation, and data analysis
                    \item Presented findings to interested local business groups
                \end{itemize}


\end{resume}
\end{document}







